Apache Storm

### 2018-02-20 paper.tex
Finalized the report

\begin{abstract}
Apache Storm is one of the available open source tools for Stream Data Processing. This document provides a brief overview of the intricacies of the Architecture of Storm and tends to proceed further on the details of considerations required to design a Solution based on Storm. The design considerations relating to deployment of Storm System as a Lambda or a Lambda-less Architecture and the sketch of the various internal components of Storm i.e. Bolts, Spouts. We consider a practical implementation of Storm to try and express the theoretical design considerations in practice. Finally we list out the other available tools and compare them to Storm with regard to Performance, Resilience and various other parameters.
\end{abstract}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{example.png}
    \caption{An Example Stream Processing Scenario}
    \label{fig:example}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{arch.png}
    \caption{Storm Physical Architecture}
    \label{fig:physicalarc}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{worker.png}
    \caption{Worker Node Architecture}
    \label{fig:workerarch}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{topo.png}
    \caption{Generic Storm Topology}
    \label{fig:communication}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{topoimpl.png}
    \caption{Topology Implementation for Sentiment Analysis}
    \label{fig:topoimpl}
   \end{center}
\end{figure}

>>>>

\begin{abstract}
Apache Storm is one of the available open source tools for Stream Data Processing. This document explores the Apache Storm architecture in detail and narrates the most important features. Resilience to faults being an important factor in Stream processing due the required availability. We consider a practical implementation of Storm to try and express the theoretical design considerations in practice. We also introduce in brief tools which are currently used in general, namely Apache Samza, Apache Spark Streaming and Apache Flimk. Compare them to Storm with regard to Performance, Resilience and various other parameters.
\end{abstract}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.85\textwidth]{example.png}
    \caption{An Example Stream Processing Scenario}
    \label{fig:example}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.85\textwidth]{arch.png}
    \caption{Storm Physical Architecture}
    \label{fig:physicalarc}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=.85\textwidth]{worker.png}
    \caption{Worker Node Architecture}
    \label{fig:workerarch}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{communication.png}
    \caption{Message flow in a Worker}
    \label{fig:communication}
   \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{topoimpl.png}
    \caption{Topology Implementation for Sentiment Analysis}
    \label{fig:topoimpl}
   \end{center}
\end{figure}
